\documentclass[parskip=half,fontsize=9pt,oneside,toc=chapterentrydotfill]{scrbook}

\include{setup}
\makeindex[columns=2, title=Recipe Index, options= -s recipeindex.ist]

\begin{document}

\pdfbookmark[part]{Cover}{cover}
\title{All Grain Homebrew Beer Recipes}
\date{\today}
\publishers{Editor: Thomas Ascher}
\dedication{Dedicated to BrauCampus Graz Hobbybrauer Stammtisch}
\maketitle

\frontmatter

\chapter*{Cheers!}

This beer recipe book was created as an homage to the BrewDog Recipe
Guide and compiled from various sources. It is not meant for the faint hearted
since it will not teach you about beer styles, ingredients, the brewing
process itself or safety measures. Books like Randy Mosher's "Mastering Home Brew"
and John Palmer's "How To Brew" will provide you with the necessary information.

All recipes in this book are organized by the National Homebrew Competition
2016 Style Guidelines and reproduced in a simplified form as faithfully
as possible. However, some information was altered for the sake of consistency,
interpreted when missing or discarded when deemed unnecessary or hard to reproduce.

Some carbonation levels specified by the following recipes exceed the safety
limits of single use or standard glass bottles. This is especially true for some
German and Belgian beer styles. Always take all necessary precautions when
bottle conditioning.

Notice of Liability: Neither the editor or contributors assume any responsibility
for the use or misuse of the presented information. It is the responsibility of
the reader to exercise good judgement and to observe all local laws and ordinances
regarding the production and consumption of alcoholic beverages.

\clearpage
\pdfbookmark[part]{Contents}{contents}
\tableofcontents

\mainmatter

% Last source: Ginger Dinger 2017 Dark Lager 

% National Homebrew Competition 2016 Style Guidelines

% -----------------------------------------------------------------------------
\stylecategory{Light Lager}
\include{americanlightlager}
\include{americanlager}
\include{internationalpalelager}
\include{munichhelles}
\include{festbier}
\include{germanhellesexportbier}

% -----------------------------------------------------------------------------
\stylecategory{Pilsner}
\include{germanleichtbier}
\include{czechpalelager}
\include{germanpils}
\include{czechpremiumpalelager}

% -----------------------------------------------------------------------------
\stylecategory{European Amber Lager}
\include{viennalager}
\include{czechamberlager}
\include{marzen}
\include{kellerbier}

% -----------------------------------------------------------------------------
\stylecategory{Dark Lager}
\include{internationaldarklager}
\include{munichdunkel}
\include{czechdarklager}
\include{schwarzbier}

% -----------------------------------------------------------------------------
\stylecategory{Bock}
\include{hellesbock}
\include{dunklesbock}
\include{doppelbock}
\include{eisbock}

% -----------------------------------------------------------------------------
\stylecategory{Light Hybrid Beer}
\include{creamale}
\include{blondeale}
\include{kolsch}
\include{americanwheat}

% -----------------------------------------------------------------------------
\stylecategory{Amber Hybrid Beer}
\include{internationalamberlager}
\include{californiacommon}
\include{altbier}

% -----------------------------------------------------------------------------
\stylecategory{English Pale Ale}
\include{ordinarybitter}
\include{bestbitter}
\include{strongbitter}

% -----------------------------------------------------------------------------
\stylecategory{Scottish \& Irish Ale}
\include{scottishlight}
\include{scottishheavy}
\include{scottishexport}
\include{irishredale}
\include{weeheavy}

% -----------------------------------------------------------------------------
\stylecategory{American Pale Ale}
\include{americanpaleale}

% -----------------------------------------------------------------------------
\stylecategory{Other American Ale}
\include{americanamberale}
\include{americanbrownale}

% -----------------------------------------------------------------------------
\stylecategory{English Brown Ale}
\include{darkmild}
\include{britishbrownale}

% -----------------------------------------------------------------------------
\stylecategory{Porter}
\include{englishporter}
\include{americanporter}
\include{balticporter}

% -----------------------------------------------------------------------------
\stylecategory{Stout}
\include{sweetstout}
\include{oatmealstout}

% -----------------------------------------------------------------------------
\stylecategory{Strong Stout}
\include{americanstout}
\include{imperialstout}

% -----------------------------------------------------------------------------
\stylecategory{American IPA}
\include{americanipa}

% -----------------------------------------------------------------------------
\stylecategory{India Pale Ale}
\include{indiapaleale}
\include{ryeipa}

% -----------------------------------------------------------------------------
\stylecategory{German Wheat \& Rye Beer}
\include{weissbier}
\include{dunklesweissbier}
\include{weizenbock}

% -----------------------------------------------------------------------------
\stylecategory{Belgian \& French Ale}
\include{witbier}
\include{belgianpaleale}
\include{saison}

% -----------------------------------------------------------------------------
%\stylecategory{Sour Ale}

% -----------------------------------------------------------------------------
\stylecategory{Belgian Strong Ale}
\include{belgianblondale}
\include{belgiangoldenstrongale}
\include{belgiandarkstrongale}

% -----------------------------------------------------------------------------
\stylecategory{Strong Ale}
\include{oldale}
\include{americanbarleywine}
\include{englishbarleywine}

% -----------------------------------------------------------------------------
\stylecategory{Fruit Beer}
\include{fruitbeer}

% -----------------------------------------------------------------------------
\stylecategory{Spice / Herb / Vegetable Beer}
\include{winterseasonalbeer}

% -----------------------------------------------------------------------------
\stylecategory{Smoke-Flavored \& Wood-Aged Beer}
\include{rauchbier}

% -----------------------------------------------------------------------------
\stylecategory{Specialty Beer}
\include{alternativesugarbeer}

\include{appendix}

\backmatter
\clearpage
\pdfbookmark[part]{Recipe Index}{index}
\printindex

\end{document}
