\part{\styleamericanale}

\begin{recipie}{Boiler Brewing Co. Bobber's Big Red Rye Pale Ale}

\begin{aboutblock}
This beer from Boiler Brewing Company was created as a collaboration with Lincoln, Nebraska,
homebrewer Bob Catherall of the world famous Lincoln Lagers Homebrew Club. The spicy rye notes
blend so perfectly with the new school Mosaic hops that it's hard to tell where the rye ends
and the hops begin. Boiler was lucky enough to win a Gold Medal at the U.S. Open Beer Championship
with the very first batch of this beer.
\end{aboutblock}

\specifications{\styleamericanale}{\galtol{5.5}}{1.058}{1.015}{5.6~\%}{40}{\srmtoebc{12.5}}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{155}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{66}}{}
\end{fermentationsteps}

\begin{directions}
Dry hop with the pellets for 3 days, then cold crash before kegging. The whole leaf Mosaic
hops go in the keg in a mesh bag for as long as the keg lasts (it won't last long). Before
racking to the keg, add the whole leaf hops, then pump up to 15 PSI with \ce{CO2}, then vent,
repeating several times to remove as much \ce{O2} as possible before racking.
\end{directions}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Simpsons Golden Promise}{\lbtokg{8}}
\malt{Flaked Rye}{\lbtokg{2}}
\malt{Melanoidin}{\lbtokg{1}}
\malt{Pale Wheat}{\lbtokg{1}}
\malt{Weyermann CARAMUNICH II}{\oztokg{8}}
\malt{Dingemans Special B}{\oztokg{8}}
\malt{Rice Hulls}{\oztokg{8}}
\end{malts}

\begin{hops}
\hop{\hopcolumbus}{11.4~\%}{\fwh}{\oztog{1}}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\hop{\hopmosaic}{11.8~\%}{\dryh{}{3~days}}{\oztog{5}}
\hop{\hopmosaic ~Cones}{8.9~\%}{\dryh{}{3~days}}{\oztog{3}}
\end{hops}

\begin{yeasts}
\yeast{Lallemand BRY-97 American West Coast Ale}
\end{yeasts}

\end{ingredientsblock}

\end{recipie}

\begin{recipie}{Boise Brewing Co. Down Down Extra Pale Ale}

\begin{aboutblock}
Inspired by a community garden, Boise Brewing has been sharing their small batch beer
with the city of Tress since 2014. Centennial hops are the main event in this pale ale -- give it a whirl!
\end{aboutblock}

\specifications{\styleamericanale}{\galtol{10}}{1.045}{}{}{40}{}{60~min}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{149}}{60~min}
\end{mashsteps}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pale}{\lbtokg{14.5}}
\malt{Crystal 15 L}{\lbtokg{2.5}}
\malt{Flaked Barley}{\oztokg{9}}
\end{malts}

\begin{hops}
\hop{\hopcentennial}{10~\%}{60~min}{\oztog{1.0}}
\hop{\hopcentennial}{10~\%}{30~min}{\oztog{0.5}}
\hop{\hopcentennial}{10~\%}{10~min}{\oztog{0.75}}
\hop{\hopcentennial}{10~\%}{\foh{}}{\oztog{1.0}}
\hop{\hopcascade}{}{\dryh{}{}}{\oztog{1.0}}
\hop{\hopcentennial}{}{\dryh{}{}}{\oztog{1.0}}
\end{hops}

\begin{yeasts}
\yeast{White Labs WLP001}
\end{yeasts}

\end{ingredientsblock}

\end{recipie}