\stylesection{\styleamericanamberale}

% -----------------------------------------------------------------------------
\begin{recipe}{Hoppy New Year Amber Ale}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Jason Bryant of Reston, VA, member of the Wort Hogs, won a silver medal in
Category \#11: Amber \& Brown American Ale with an American Amber Ale during the
2019 National Homebrew Competition Final Round in Providence, RI. Bryant's American
Amber Ale was chosen as the runner-up entry among 281 entries in the category.
\sourceaha
\end{aboutblock}

\specifications{\styleamericanamberale}{\galtol{6.5}}{1.058}{1.011}{5.7~\%}{65.3}{\srmtoebc{12.3}}{90~min}{2.5}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{156}}{}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{65}}{}
\end{fermentationsteps}

\begin{directions}
Acidify sparge water to pH 5.6 with lactic acid. Target pH of 5.2 to 5.5.
Chill to \ftoc{195} before adding the whirlpool hops.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pilsner}{\lbtokg{8.5}}
\malt{Pale}{\lbtokg{1.8}}
\malt{Weyermann Munich II}{\oztokg{11.8}}
\malt{Aromatic}{\oztokg{7.2}}
\malt{Weyermann CARAAMBER}{\oztokg{7.2}}
\malt{Caramel / Crystal 20 L}{\oztokg{7.2}}
\malt{Caramel / Crystal 120 L}{\oztokg{7.2}}
\malt{Weyermann CARARED}{\oztokg{7.2}}
\malt{Caravienne}{\oztokg{7.2}}
\malt{Simpsons Dark Crystal}{\oztokg{7.2}}
\end{malts}

\begin{hops}
\hop{\hopsummit}{19~\%}{90~min}{\oztog{0.2}}
\hop{\hopcitra}{11.1~\%}{5~min}{\oztog{0.4}}
\hop{\hopidahoseven}{11.6~\%}{5~min}{\oztog{0.4}}
\hop{\hopcitra}{11.1~\%}{\whirl{}{15~min}}{\oztog{1.2}}
\hop{\hopidahoseven}{11.6~\%}{\whirl{}{15~min}}{\oztog{1.2}}
\hop{\hopsummit}{19~\%}{\whirl{}{15~min}}{\oztog{0.7}}
\hop{\hoppalisade ~Cryo}{14~\%}{\whirl{}{15~min}}{\oztog{0.4}}
\end{hops}

\singleyeast{American Ale}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Iron Monk Brewing Co. Velvet Antler Amber Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Iron Monk Brewing's American amber ale is very malt forward and smooth. They
hear from fans all the time that this is their all-time favorite beer, and we think
you’ll agree once you brew some yourself. \sourceaha
\end{aboutblock}

\specifications{\styleamericanamberale}{\galtol{5}}{1.045}{}{4.6~\%}{14}{}{60~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{60~min}
\mashstep{\ftoc{170}}{10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{68}}{}
\end{fermentationsteps}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Two-row}{\lbtokg{7}}
\malt{Caramel / Crystal 60 L}{\lbtokg{2}}
\malt{Munich Light}{\lbtokg{0.5}}
\malt{Red}{\lbtokg{0.5}}
\malt{Flaked Wheat}{\lbtokg{0.5}}
\malt{Flaked Barley}{\lbtokg{0.5}}
\end{malts}

\begin{hops}
\hop{\hopsimcoe}{}{60~min}{\oztog{0.4}}
\hop{\hopcascade}{}{\foh{}}{\oztog{0.3}}
\end{hops}

\singleyeast{Fermentis SafAle S-05}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Kilauea Punch American Amber Ale}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Derek Springer of San Marcos, CA, member of the Society of Barley Engineers,
won a bronze medal in Category \#11: Amber \& Brown American Ale with an
American Amber Ale during the 2019 National Homebrew Competition Final Round
in Providence, RI. Springer's American Amber Ale was chosen as a top three
entry among 281 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleamericanamberale}{\galtol{5.5}}{1.057}{1.015}{5.6~\%}{180.9}{\srmtoebc{14.7}}{}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{153}}{60~min}
\mashstep{\ftoc{168}}{10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{65}}{1~day}
\fermentationstep{\ftoc{68}}{6~days}
\fermentationstep{\ftoc{32}}{1~day}
\end{fermentationsteps}

\begin{directions}
After 4 days add dry hops. After fermentation add gelatin and a day after that
keg and carbonate.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Great Western Premium Two-row}{\lbtokg{4}}
\malt{Crisp Maris Otter}{\lbtokg{4}}
\malt{Weyermann Munich II}{\oztog{16}}
\malt{Dingemans Biscuit}{\oztog{8}}
\malt{Great Western Crystal 120}{\oztog{8}}
\malt{Great Western Crystal 40}{\oztog{8}}
\malt{Great Western Crystal 75}{\oztog{8}}
\end{malts}

\begin{hops}
\hop{\hopgalaxy}{18.1~\%}{15~min}{\oztog{1}}
\hop{\hopcentennial}{10.4~\%}{5~min}{\oztog{1}}
\hop{\hopmotueka}{7.3~\%}{5~min}{\oztog{1}}
\hop{\hopcentennial}{10.4~\%}{\dryh{}{3~days}}{\oztog{1}}
\hop{\hopgalaxy}{18.1~\%}{\dryh{}{3~days}}{\oztog{1}}
\hop{\hopmotueka}{7.3~\%}{\dryh{}{3~days}}{\oztog{1}}
\end{hops}

\singleyeast{White Labs WLP090}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Possibility and Promise Pacific Amber}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Justin Westcott of Federal Way, WA, member of the Browns Point Homebrew Club, won
a gold medal in Category \#11: Amber \& Brown American Ale with an American Amber
Ale during the 2019 National Homebrew Competition Final Round in Providence, RI.
Westcott's Amber \& Brown American Ale was chosen as the best among 281 entries in
the category. \sourceaha
\end{aboutblock}

\specifications{\styleamericanamberale}{\galtol{5.2}}{1.057}{1.011}{6.1~\%}{35}{\srmtoebc{11}}{60~min}{2.6}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{152}}{60~min}
\mashstep{\ftoc{168}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{64}}{2~weeks}
\end{fermentationsteps}

\begin{directions}
Condition at \ftoc{65} for 1 month.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pale}{\lbtokg{10}}
\malt{Weyermann CARARED}{\lbtokg{2.2}}
\malt{Caramel / Crystal 80 L}{\oztog{8}}
\malt{Weyermann Melanoidin}{\oztog{8}}
\end{malts}

\begin{hops}
\hop{\hopcascade}{7.8~\%}{60~min}{\oztog{0.5}}
\hop{\hopcentennial}{8~\%}{20~min}{\oztog{0.5}}
\hop{\hopcascade}{7.8~\%}{15~min}{\oztog{0.5}}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\hop{Yeast Nnutrient}{}{15~min}{2.2~g}
\hop{\hopamarillo}{7.7~\%}{5~min}{\oztog{1}}
\hop{\hopcentennial}{8~\%}{5~min}{\oztog{0.5}}
\end{hops}

\singleyeast{Imperial Yeast A07}

\end{ingredientsblock}

\end{recipe}