\stylesection{\styleamericanstout}

% -----------------------------------------------------------------------------
\begin{recipe}{Rogue Chocolate Stout Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Many chocolate stouts seem to have acidic coffee flavors and end up falling short
of real chocolate flavor. However, Rogue's Chocolate Stout is smooth, sweet and
velvety, and tastes like a chocolate malted milkshake with slight hoppiness and
bittersweet chocolate notes. The allure of this beer comes down to the chocolate
flavors, which makes it enjoyable for both the chocolate and beer lover. The sweet,
creamy head gives way to a rich chocolate truffle finish. This beer pairs perfectly
with desserts as it's balanced by plenty of roasty flavor and bitterness.
\sourcezymurgy{July / August 2009}
\end{aboutblock}

\specifications{\styleamericanstout}{\galtol{5}}{1.069}{1.017}{6.8~\%}{30}{\srmtoebc{25}}{90~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{150}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{60}}{1~week}
\fermentationstep{\ftoc{50}}{Transfer to secondary; util fully attenuated}
\end{fermentationsteps}

\begin{directions}
Siphon into secondary at \ftoc{50} onto chocolate extract and hold until
fermentation is complete, then package and condition.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Great Western Premium Tow-row}{\lbtokg{11}}
\malt{Caramel / Crystal 120 L}{\lbtokg{0.5}}
\malt{Chocolate}{\lbtokg{0.5}}
\malt{Rolled Oats}{\lbtokg{0.5}}
\malt{Roast Barley}{\oztokg{3}}
\end{malts}

\begin{hops}
\hop{\hopcascade}{5~\%}{90~min}{\oztog{1}}
\hop{\hopcascade}{5~\%}{30~min}{\oztog{1}}
\hop{Irish Moss}{}{20~min}{\tsptoml{1}}
\hop{\hopcascade}{5~\%}{\foh{}}{\oztog{1}}
\end{hops}

\singleyeast{Wyeast 1764-PC / White Labs WLP001}

\begin{twists}
\twist{Chocolate Extract}{Secondary}{\oztog{1.51}}
\end{twists}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Stout Trousers}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Chris O'Brien is a homebrewer with a mission: How to Drink
Beer and Save the World, O'Brien takes homebrewing to the next level
by promoting the use of responsibly cultivated, organic ingredients.
"Making organic homebrew is no different than making regular homebrew.
Just start with fresh, organic ingredients and the rest is the art and
science of homebrewing -- same as usual. The one big challenege is finding those
ingredients." Of course, if you can't get your hands on strictly
organic ingredients, Stout Trousers -- a deliciously hoppy American
stout -- can still be brewed with non-organic substitutes.
\sourcezymurgy{March / April 2009}
\end{aboutblock}

\specifications{\styleamericanstout}{\galtol{5}}{1.072}{1.018}{7.1~\%}{}{}{100~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{64}}{1~day}
\fermentationstep{\ftoc{66}}{Until 75~\% attenuated}
\fermentationstep{\ftoc{70}}{1~week}
\fermentationstep{\ftoc{40}}{2~days}
\end{fermentationsteps}

\begin{directions}
Water adjustment: do not use soft water for this brew. Acidify the strike water
to a pH of 4.8. This should result in a mash pH of 5.2. Also acidify the sparge
water to 4.8.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Great Western Organic Premium Two-row}{\lbtokg{11.5}}
\malt{Briess Organic Roasted Barley}{\lbtokg{0.75}}
\malt{Briess Organic Chocolate}{\oztokg{8.8}}
\malt{Briess Organic Caramel 60 L}{\oztokg{8.8}}
\malt{Weyermann CARAFA II}{\oztokg{3.2}}
\end{malts}

\begin{hops}
\hop{\hoppacificgem}{}{60~min}{\oztog{0.75}}
\hop{\hopfuggle}{}{15~min}{\oztog{1.5}}
\hop{\hopcascade}{}{10~min}{\oztog{1.5}}
\hop{Irish Moss}{}{10~min}{\tsptoml{1}}
\hop{\hopcascade}{}{5~min}{\oztog{1}}
\end{hops}

\singleyeast{Wyeast 1272}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{The Singularity Stout}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Divesh Lakhi of Cedar Rapids, IA, won a bronze medal in Category \#14: American
Porter \& Stout with an American Stout during the 2019 National Homebrew
Competition Final Round in Providence, RI. Lakhi's American Stout was chosen as
a top three entry among 304 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleamericanstout}{\galtol{5.25}}{1.064}{1.017}{6.17~\%}{51}{\srmtoebc{38.5}}{60~min}{2.2}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{66}}{}
\end{fermentationsteps}

\begin{directions}
Let condition for 2 weeks after fermentation is complete.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Simpsons Golden Promise}{\lbtokg{10}}
\malt{White Wheat}{\lbtokg{0.5}}
\malt{Flaked Barley}{\lbtokg{0.5}}
\malt{Munich}{\lbtokg{0.5}}
\malt{Briess Victory}{\lbtokg{0.5}}
\malt{Caramel / Crystal 60 L}{\lbtokg{0.4375}}
\malt{Caramel / Crystal 120 L}{\lbtokg{0.3125}}
\malt{Chocolate}{\lbtokg{0.75}}
\malt{Roasted Barley}{\lbtokg{0.625}}
\malt{Briess Black Patent}{\lbtokg{0.125}}
\end{malts}

\begin{hops}
\hop{\hopnugget}{13.6~\%}{60~min}{\oztog{0.8}}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\hop{\hopeastkentgolding}{4.4~\%}{10~min}{\oztog{3.25}}
\end{hops}

\singleyeast{White Labs WLP001}

\end{ingredientsblock}

\end{recipe}
