\stylesection{\stylebelgiangoldenstrongale}

% -----------------------------------------------------------------------------
\begin{recipie}{Nuetnigenough Belgian Golden Strong}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Wesley Carmichael \& Mandy Naglich of New York, NY, won a silver medal in
Category \#22: Strong Belgian Ale with a Belgian Golden Strong Ale during the
2019 National Homebrew Competition Final Round in Providence, RI. Carmichael's
Belgian Golden Strong Ale was chosen as the runner-up entry among 389 entries
in the category. \sourceaha
\end{aboutblock}

\specifications{\stylebelgiangoldenstrongale}{\galtol{6}}{1.071}{1.010}{8.9~\%}{27}{\srmtoebc{3.3}}{90~min}{3}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{30~min}
\mashstep{\ftoc{170}}{Raise to over 4~min; 10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{60}}{Until activity slows}
\fermentationstep{\ftoc{75}}{Until fully attenuated}
\end{fermentationsteps}

\begin{directions}
Cold crash with gelatin when fully attenuated. Bottle condition with priming
sugar.
\end{directions}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Dingemans Pilsen}{\lbtokg{9.7}}
\malt{Flaked Wheat}{\oztog{16}}
\malt{Weyermann Acidulated}{\oztog{7}}
\end{malts}

\begin{hops}
\hop{Dextrose}{}{}{\lbtokg{2.7}}
\hop{\hopmagnum}{14~\%}{90~min}{\oztog{0.6}}
\hop{\hopsaaz}{3.8~\%}{5~min}{\oztog{1}}
\hop{\hopstyriangolding}{5.4~\%}{5~min}{\oztog{1}}
\hop{\hopsaaz}{3.8~\%}{\whirl{}{}}{\oztog{1}}
\hop{\hopstyriangolding}{5.4~\%}{\whirl{}{}}{\oztog{1}}
\end{hops}

\singleyeast{Wyeast 1388}

\end{ingredientsblock}

\end{recipie}

% -----------------------------------------------------------------------------
\begin{recipie}{Ozark Beer Co. Belgian Golden Ale Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Ozark Beer Co. brews this traditional Belgian-style golden ale with pilsen malt
and noble hops that lend aromas of apples and pears. The perfectly timed hop
additions makes it a light, dry and very refreshing homebrew. \sourceaha
\end{aboutblock}

\specifications{\stylebelgiangoldenstrongale}{\galtol{5}}{1.055}{1.004}{6.7~\%}{33}{\srmtoebc{3.4}}{75~min}{2.6}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{152}}{30~min}
\mashstep{\ftoc{170}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{80}}{}
\end{fermentationsteps}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Briess Pilsner}{\lbtokg{6}}
\malt{Briess Pale Ale}{\lbtokg{2.33}}
\malt{Briess White Wheat}{\lbtokg{4.8}}
\malt{Briess Raw White Wheat}{\lbtokg{4.8}}
\malt{Weyerman Acidulated}{\lbtokg{4.8}}
\end{malts}

\begin{hops}
\hop{\hopsterling}{8.4~\%}{60~min}{\oztog{0.6}}
\hop{\hopsterling}{8.4~\%}{45~min}{\oztog{0.6}}
\hop{Yeast Nutrient}{}{15~min}{1.6~g}
\hop{Whirlfloc Tablet}{}{10~min}{1}
\hop{\hopsterling}{8.4~\%}{5~min}{\oztog{0.6}}
\end{hops}

\singleyeast{Omega Yeast OYL-500}

\end{ingredientsblock}

\end{recipie}

