\stylesection{\styleimperialstout}

% -----------------------------------------------------------------------------
\begin{recipe}{Bourbon Barrel Aged Full Eclipse II}
% -----------------------------------------------------------------------------

\begin{aboutblock}
A silver-medal-winning imperial stout recipe from the 2017 National Homebrew
Competition courtesy of brewers Ryan Golden and Matt Warren of Signal Mountain, TN.
With help from their club Barley Mob Brewers and BeerSmith, they've created a
intricate and delicious recipe sure to warm any cold winter hands. \sourceaha
\end{aboutblock}

\specifications{\styleimperialstout}{\galtol{12}}{1.124}{1.030}{}{}{}{120~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{153}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{65}}{}
\end{fermentationsteps}

\begin{directions}
When fully attenuated, transfer to a bourbon barrel and age until the desired amount
of oak and bourbon character is reached.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Rice Hulls}{\lbtokg{1}}
\malt{Maris Otter}{\lbtokg{40}}
\malt{Flaked Wheat}{\lbtokg{5}}
\malt{Pale Chocolate}{\lbtokg{4}}
\malt{Chocolate}{\lbtokg{3}}
\malt{Roasted Barley}{\lbtokg{3}}
\malt{Dingemans Special B}{\lbtokg{3}}
\malt{Caramel / Crystal 120 L}{\lbtokg{1}}
\end{malts}

\begin{hops}
\hop{\hopmagnum}{12.3}{90~min}{\oztog{5.5}}
\hop{\hopfuggle}{4.2}{20~min}{\oztog{2}}
\hop{\hopstyriangolding}{3.4}{20~min}{\oztog{2}}
\hop{Whirlfloc Tablet}{}{5~min}{1}
\hop{\hopfuggle}{4.2}{\whirl{}{15~min}}{\oztog{2}}
\hop{\hopstyriangolding}{3.4}{\whirl{}{15~min}}{\oztog{2}}

\end{hops}

\singleyeast{Wyeast 1028}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Mill 'em All Imperial Stout}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Tim Hill of St. Louis, MO, member of the STL Hops, won a silver medal
in Category \#15: Imperial Stout during the 2019 National Homebrew Competition
Final Round in Providence, RI. Hill's Imperial Stout was chosen as the runner-up
entry among 226 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleimperialstout}{\galtol{5.25}}{1.104}{1.031}{9.8~\%}{78}{\srmtoebc{65}}{120~min}{2.2}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{156}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{66}}{2~weeks}
\end{fermentationsteps}

\begin{directions}
Allow another 6 weeks in primary before packaging.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Two-row}{\lbtokg{14.25}}
\malt{Flaked Oats}{\lbtokg{2.75}}
\malt{Caramel / Crystal 60 L}{\lbtokg{1.25}}
\malt{Caramel / Crystal 120 L}{\lbtokg{1.25}}
\malt{Roasted Barley}{\lbtokg{1.13}}
\malt{Briess Black Patent}{\oztokg{10}}
\malt{Chocolate}{\oztokg{10}}
\end{malts}

\begin{hops}
\hop{\hoppolaris}{19~\%}{60~min}{\oztog{1.5}}
\hop{\hoppolaris}{19~\%}{20~min}{\oztog{0.35}}
\hop{Light Brown Sugar}{}{}{\oztog{8}}
\end{hops}

\singleyeast{Fermentis SafAle US-05}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Richard's Brownie Batter Imperial Stout}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Tom Lawrence of San Diego, CA, won a gold medal in Category \#25: Spiced Beer with
an Imperial Stout with Coconut and Coffee during the 2019 National Homebrew Competition
Final Round in Providence, RI, with the help of Zach Dixon. Lawrence and Dixon's Spiced
Beer, am imperial stout made with coconut and coffee, was chosen as the best among 430
entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleimperialstout}{\galtol{3}}{1.093}{1.030}{8.3~\%}{52}{\srmtoebc{40}}{240~min}{2.2}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{150}}{60~min}
\mashstep{\ftoc{170}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{66}}{3~days}
\fermentationstep{\ftoc{72}}{Raise to by 0.5~°C/day; 28~days}
\fermentationstep{\ftoc{72}}{Transfer to secondary; 2~weeks}
\end{fermentationsteps}

\begin{directions}
Water adjustment: \waterprofile{53}{5}{61}{37}{45}{217}. Lightly toast shredded
coconut on the stove until light brown in color and let cool. Put coconut and
coffee beans in a muslin bag. Let beer condition on coconut and coffee at least
2 weeks.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Maris Otter}{\lbtokg{6}}
\malt{Weyermann CARAFA II}{\lbtokg{0.69}}
\malt{Briess Midnight Wheat}{\lbtokg{0.69}}
\malt{Flaked Oats}{\lbtokg{0.69}}
\malt{BEST Chit}{\lbtokg{0.69}}
\malt{Caramel / Crystal 10 L}{\lbtokg{0.69}}
\malt{Caramel / Crystal 20 L}{\lbtokg{0.5}}
\malt{Caramel / Crystal 40 L}{\lbtokg{0.5}}
\malt{Caramel / Crystal 60 L}{\oztog{3.04}}
\malt{Caramel / Crystal 80 L}{\oztog{3.04}}
\malt{Caramel / Crystal 120 L}{\oztog{3.04}}
\end{malts}

\begin{hops}
\hop{\hopmosaic}{}{240~min}{\oztog{1}}
\end{hops}

\singleyeast{RVA Yeast Labs RVA 132}

\begin{twists}
\twist{Coconut (Medium Toast)}{Secondary}{\lbtokg{1.5}}
\twist{Whole Arabica Coffee Beans}{Secondary}{\oztog{0.5}}
\end{twists}

\end{ingredientsblock}

\end{recipe}
