\stylesection{\stylemunichhelles}

% -----------------------------------------------------------------------------
\begin{recipie}{Brewin' in Maillard Helles}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Russell Berger of Portland, OR, member of the Portland Brewers Collective, won
a bronze medal in Category \#2: Pale European Beer with a German Helles Exportbier
during the 2019 National Homebrew Competition Final Round in Providence, RI.
Berger's German Helles Exportbier was chosen as a top three entry among 394
entries in the category. \sourceaha
\end{aboutblock}

\specifications{\stylemunichhelles}{\galtol{6}}{1.054}{1.010}{6.5~\%}{22}{\srmtoebc{5}}{90~min}{2.7}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{131}}{15~min}
\mashstep{\ftoc{148}}{30~min}
\mashstep{\ftoc{160}}{30~min}
\mashstep{\ftoc{168}}{10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{52}}{Until attenauted to \sgtop{1.030}}
\fermentationstep{\ftoc{57}}{Until attenuated to \sgtop{1.016}}
\fermentationstep{\ftoc{62}}{Until fully attenuated}
\fermentationstep{\ftoc{32}}{Slowly reduce to}
\end{fermentationsteps}

\begin{directions}
Bring mash pH to 5.2. Once the beer has reached \ftoc{32}, fine with
gelatin and lager for 4 weeks.
\end{directions}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{BEST Heidelberg}{\lbtokg{3.85}}
\malt{Weyermann Pilsner}{\lbtokg{3.85}}
\malt{Great Western Pure Idaho}{\lbtokg{3.75}}
\malt{Weyermann Melanoidin}{\lbtokg{0.25}}
\malt{Weyermann Munich I}{\lbtokg{0.65}}
\malt{Wyeast BrewTan B}{--}
\end{malts}

\begin{hops}
\hop{\hoptettnang}{4.4~\%}{\fwh}{\oztog{1.75}}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\hop{Yeast Nutrient}{}{10~min}{--}
\end{hops}

\singleyeast{Imperial Yeast L17}

\end{ingredientsblock}

\end{recipie}

% -----------------------------------------------------------------------------
\begin{recipie}{Helicious Helles}
% -----------------------------------------------------------------------------

\begin{aboutblock}
This Munich helles lager earned Kerry Martin the best of show title in the 2010
Lunar Rendezbrew XVII homebrew competition. A member of the Austin Zealots club,
Martin used his brewing experience and resources to mimic a recipe from the
Brewing Network's Jamil Zainasheff. Martin adds that he "added acidulated
malt and thinks it gives it a little zip and helps with keeping the mash pH in
the optimum range with the light malt bill." \sourceaha
\end{aboutblock}

\specifications{\stylemunichhelles}{\galtol{7}}{1.050}{1.012}{5~\%}{19.1}{}{90~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{130}}{10~min}
\mashstep{\ftoc{148}}{60~min}
\mashstep{\ftoc{168}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{50}}{2--3~weeks}
\end{fermentationsteps}

\begin{directions}
Add gelatin to clarify. Lager at \ftoc{40} for 3--6 weeks.
\end{directions}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pilsner}{\lbtokg{9.5}}
\malt{Torrified Wheat}{\lbtokg{1}}
\malt{Weyermann Melanoidin}{\oztog{5}}
\malt{Acidulated}{\oztog{7}}
\end{malts}

\begin{hops}
\hop{\hoptettnang}{4~\%}{60~min}{\oztog{1.9}}
\hop{Whirlfloc Tablet}{}{10~min}{1}
\end{hops}

\singleyeast{Wyeast 2247-PC / White Labs 830 / White Labs 833}

\end{ingredientsblock}

\end{recipie}

% -----------------------------------------------------------------------------
\begin{recipie}{Hot Schnitzel}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Metts Potter of Browns Summit, NC, member of the Battleground Brewers Guild, the winning
club of the 2019 Gambrinus Club Award, won a silver medal in Category \#2: Pale European
Beer with a Munich Helles during the 2019 National Homebrew Competition Final Round in
Providence, RI. Potter's Munich Helles was chosen as the runner-up entry among 394 entries in the category. \sourceaha 
\end{aboutblock}

\specifications{\stylemunichhelles}{\galtol{5.5}}{1.050}{1.010}{5.2~\%}{18}{\srmtoebc{4.5}}{90~min}{2.5}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{151}}{60~min}
\mashstep{\ftoc{170}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{50}}{5~days / fermentation start}
\fermentationstep{\ftoc{70}}{Raise to over 4~days; 5~days}
\end{fermentationsteps}

\begin{directions}
Mash at 5.3 pH. Clarify with gelatin.
\end{directions}

\end{methodandtiming}

\pagebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Weyermann Pilsner}{\lbtokg{4}}
\malt{Weyermann Barke Pilsner}{\lbtokg{4}}
\malt{Bestmalz Munich}{\lbtokg{1}}
\malt{Weyermann CARAFOAM}{\oztog{4}}
\malt{Weyermann CARAHELL}{\oztog{2}}
\end{malts}

\begin{hops}
\hop{\hoptettnang}{3.2~\%}{\fwh}{1}
\hop{\hoptettnang}{3.2~\%}{15~min}{1}
\end{hops}

\singleyeast{White Labs WLP838}

\end{ingredientsblock}

\end{recipie}

