\stylesection{\styleschwarzbier}

% -----------------------------------------------------------------------------
\begin{recipe}{May the Schwartz Be With You}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Frank Taddeo of Royersford, PA, member of the Bruclear Homebrew Club, won a gold
medal in Category \#5: Dark European Lager with a Schwarzbier during the 2019
National Homebrew Competition Final Round in Providence, RI. Taddeo's Dark European
Lager was chosen as the best among 241 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleschwarzbier}{\galtol{5.5}}{1.056}{1.015}{5.3~\%}{30}{\srmtoebc{28}}{90~min}{2}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{45~min}
\mashstep{\ftoc{170}}{Mashout}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{50}}{5~days}
\fermentationstep{\ftoc{65}}{Raise to over 2~days; 2~days}
\fermentationstep{\ftoc{50}}{Reduce to over 2~days}
\end{fermentationsteps}

\begin{directions}
Target mash pH of 5.3. Chill to \ftoc{170} before adding the whirlpool hops.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Dark Munich}{\lbtokg{6}}
\malt{Pilsner}{\lbtokg{6}}
\malt{Chocolate}{\oztog{6}}
\malt{Caramel / Crystal 40 L}{\oztog{6}}
\malt{Roast Barley}{\oztog{3.5}}
\malt{Weyerman CARAFA SPECIAL II}{\oztog{3.5}}
\malt{Acidulated}{\oztog{2}}
\end{malts}

\begin{hops}
\hop{\hophallertaumittelfruh}{4~\%}{60~min}{\oztog{1.4}}
\hop{\hophallertaumittelfruh}{4~\%}{20~min}{\oztog{0.5}}
\hop{\hophallertaumittelfruh}{4~\%}{\whirl{}{10~min}}{\oztog{0.5}}
\end{hops}

\singleyeast{Wyeast 2206}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Red Rock Brewing Black Bier Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
This beer recipe was taken from the book Session Beers: Brewing for Flavor and
Balance by Jennifer Talley. This German-style dark lager from Red Rock Brewery
is a classic schwarzbier that won a gold medal at the 2010 Great American Beer
Festival. It's unusually dark color is gained from four different malts and very
light hopping that make it a sessionable black lager. \sourceaha
\end{aboutblock}

\specifications{\styleschwarzbier}{\galtol{5}}{1.040}{1.009}{4~\%}{28}{}{60~min}{2.5}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{148}}{}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{48}}{}
\end{fermentationsteps}

\begin{directions}
Use reverse osmosis water pH with lactic acid, no calcium needed.
Age in the coldest place you have, \ftoc{33}--\ftoc{36} is optimal. Since it's
only 4~\% ABV do not cool below \ftoc{33}.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pilsner}{\lbtokg{7}}
\malt{Munich}{\oztokg{12}}
\malt{Dehusked Black}{\oztokg{5}}
\malt{Roast}{\oztokg{1.5}}
\end{malts}

\begin{hops}
\hop{\hoptettnang}{4~\%}{60~min}{\oztog{0.75}}
\hop{\hoptettnang}{4~\%}{30~min}{\oztog{0.75}}
\hop{\hophallertaumittelfruh}{4~\%}{\whirl{}{}}{\oztog{1.5}}
\end{hops}

\singleyeast{Wyeast 2124}

\end{ingredientsblock}

\end{recipe}
