\stylesection{\stylesweetstout}

% -----------------------------------------------------------------------------
\begin{recipe}{Belgian Dip Chocolate Stout}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Recipe by Amahl Turczyn based off of Mountain Sun Pub \& Brewery's
(Boulder, CO) chocolate stout. Has sweet chocolaty notes.
\sourcezymurgy{November / December 2007}
\end{aboutblock}

\specifications{\stylesweetstout}{\galtol{5}}{1.072}{}{}{}{\srmtoebc{45}}{90~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{60~min}
\end{mashsteps}

\begin{directions}
Add lactose to kettle before running clear wort into the kettle. Coarsely chop
chocolate and add to wort after boil is complete.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pale}{\lbtokg{8.87}}
\malt{Black Barley}{\lbtokg{0.81}}
\malt{Briess Bonlander Munich 10 L}{\lbtokg{0.81}}
\malt{Briess Caramel Vienne 20 L}{\lbtokg{0.56}}
\malt{Brown}{\lbtokg{0.48}}
\malt{Briess Victory}{\lbtokg{0.48}}
\malt{Wheat}{\lbtokg{0.32}}
\malt{Chocolate}{\lbtokg{0.24}}
\malt{Chocolate Rye}{\lbtokg{0.24}}
\end{malts}

\begin{hops}
\hop{Lactose}{}{\fwh}{\lbtokg{0.89}}
\hop{\hophallertaumittelfruh}{}{60~min}{\oztog{0.65}}
\hop{\hopliberty}{}{\foh{}}{\oztog{0.52}}
\hop{Callebaut Milk Chocolate}{}{\foh{}}{\lbtokg{0.53}}
\hop{Callebaut Dark Chocolate}{}{\foh{}}{\lbtokg{0.18}}
\end{hops}

\singleyeast{Mountain Sun Ale / American Ale}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Nortons Brewing Co. Don't Poke the Bear Milk Stout Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
A chocolate imperial milk stout with vanilla. \sourceaha
\end{aboutblock}

\specifications{\stylesweetstout}{\galtol{5}}{1.096}{1.035}{8.2~\%}{17.1}{\srmtoebc{38.3}}{60~min}{}

\begin{methodandtiming}

\begin{mashsteps}
\mashstep{\ftoc{152}}{60~min}
\mashstep{\ftoc{168}}{10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{68}}{}
\end{fermentationsteps}

\begin{directions}
Add coca nibs after 75~\% of fermentation is complete. Create a tincture out of vanilla
beans at brew day.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Bairds Maris Otter Pale Ale}{\lbtokg{12}}
\malt{Rahr White Wheat}{\lbtokg{1.3}}
\malt{Weyermann Munich I}{\oztog{11.5}}
\malt{Crisp Chocolate}{\oztog{9.7}}
\malt{Flaked Oats}{\oztog{9.6}}
\malt{Flaked Barley}{\oztog{9.6}}
\malt{Crisp Roasted Barley}{\oztog{7.8}}
\end{malts}

\begin{hops}
\hop{\hopgalena}{12.5~\%}{60~min}{\oztog{0.4}}
\hop{Dutch Cocoa}{}{30~min}{\oztog{1}}
\hop{Lactose}{}{20~min}{\lbtokg{1.5}}
\hop{\hopmthood}{6~\%}{15~min}{\oztog{0.9}}
\end{hops}

\singleyeast{Wyeast 1028}

\begin{twists}
\twist{Cocoa Nibs}{Primary}{\oztog{6}}
\twist{Cold Brew Coffee}{Secondary}{\oztoml{2}}
\twist{Vanilla Beans}{Secondary (1~week)}{2}
\end{twists}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Outlaw Brewing Udder Madness Chocolate Milk Stout Clone}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Full body and rich mouthfeel. \sourceaha
\end{aboutblock}

\specifications{\stylesweetstout}{\galtol{5}}{1.058}{1.014}{5.7~\%}{21}{}{60~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{152}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{68}}{Until attenuated to \sgtop{1.024}}
\fermentationstep{\ftoc{70}}{Free raise to; until fully attenuated}
\end{fermentationsteps}

\begin{directions}
After diacetyl rest, remove from yeast and cold crash. Add chocolate of
choice (Outlaw Brewing prefers an organic cocao at a rate of \ozpgaltogpl{6}.
Swirl fermenter periodically for first day, then allow to settle for 4 days.
Transfer off chocolate, carbonate, and enjoy!
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}
 
\begin{malts}
\malt{Two-row}{\lbtokg{5}}
\malt{Flaked Wheat}{\oztog{10}}
\malt{Caramel / Crystal 45 L}{\oztog{6}}
\malt{Chocolate}{\oztog{6}}
\malt{Flaked Oats}{\oztog{5}}
\malt{Roasted Barley}{\oztog{3.7}}
\end{malts}

\begin{hops}
\hop{\hopnorthernbrewer}{}{60~min}{\oztog{0.4}}
\hop{Lactose}{}{10~min}{\oztog{5}}
\hop{\hopfuggle}{}{5~min}{\oztog{0.4}}
\end{hops}

\singleyeast{American Ale}

\begin{twists}
\twist{Chocolate}{Secondary (5~days)}{\oztog{30}}
\end{twists}

\end{ingredientsblock}

\end{recipe}

