\stylesection{\styleviennalager}

% -----------------------------------------------------------------------------
\begin{recipe}{American Vienna Lager}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Kevin Lemme of Carmel, IN, won a bronze medal in Category \#4: Amber European Beer with
a Vienna Lager during the 2019 National Homebrew Competition Final Round in Providence,
RI. Lemme's Vienna Lager was chosen as a top three entry among 365 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleviennalager}{\galtol{10}}{1.050}{1.012}{5.1~\%}{20}{\srmtoebc{10}}{90~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{125}}{30~min}
\mashstep{\ftoc{147}}{30~min}
\mashstep{\ftoc{162}}{30~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{52}}{5~days}
\fermentationstep{\ftoc{58}}{3~days}
\fermentationstep{\ftoc{62}}{3~days}
\fermentationstep{\ftoc{50}}{When fully attenuated reduce to by 1~°C/day}
\end{fermentationsteps}

\begin{directions}
Lager for 3 months.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Pilsner}{\lbtokg{8}}
\malt{Vienna}{\lbtokg{8}}
\malt{Dark Munich}{\lbtokg{2.5}}
\malt{Weyermann CARAAMBER}{\lbtokg{2.5}}
\end{malts}

\begin{hops}
\hop{\hopnorthernbrewer}{}{60~min}{\oztog{7.5}}
\hop{\hopsaaz}{}{20~min}{\oztog{3.5}}
\hop{Yeast Nutrient}{}{15~min}{--}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\end{hops}

\singleyeast{Imperial Yeast L17}

\end{ingredientsblock}

\end{recipe}

% -----------------------------------------------------------------------------
\begin{recipe}{Lovelace Vienna Lager}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Robert Lovelace of Denver, NC, member of Fermentation Nation, won a gold medal in
Category 4: Amber European Beer during the 2018 National Homebrew Competition Final
Round in Portland, OR. Lovelace's Vienna lager was chosen as best among 273 entries
in the category. \sourceaha
\end{aboutblock}

\specifications{\styleviennalager}{\galtol{6.5}}{1.052}{1.013}{5.2~\%}{31}{\srmtoebc{28}}{60~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{144}}{30~min}
\mashstep{\ftoc{158}}{30~min}
\mashstep{\ftoc{170}}{10~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{48}}{10~days}
\fermentationstep{\ftoc{58}}{Raise to over 4~days}
\end{fermentationsteps}

\begin{directions}
Use low-mineral tap water. No sparge. Add lactic acid for 5.2 pH if needed. Lager
and carbonate at \ftoc{36} for 2 weeks until clear.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Weyermann Pilsner}{\lbtokg{6.5}}
\malt{Weyermann Vienna}{\lbtokg{5}}
\malt{Weyermann Munich II}{\lbtokg{1.5}}
\malt{Briess Victory}{\oztokg{8}}
\malt{Weyermann CARAAMBER}{\oztokg{8}}
\malt{Briess Blackprinz}{\lbtokg{0.15}}
\end{malts}

\begin{hops}
\hop{\hopmagnum}{14~\%}{60~min}{\oztog{0.63}}
\hop{\hoptettnang}{3.5~\%}{\foh{}}{\oztog{1}}
\hop{Whirlfloc Tablet}{}{\foh{}}{1}
\end{hops}

\singleyeast{White Labs WLP830}

\end{ingredientsblock}

% -----------------------------------------------------------------------------
\begin{recipe}{Viva! Vienna!}
% -----------------------------------------------------------------------------

\begin{aboutblock}
Tim Gerbracht of Vienna, VA, member of GRiST, won a silver medal in Category
\#4: Amber European Beer with a Vienna Lager during the 2019 National Homebrew
Competition Final Round in Providence, RI. Gerbracht's Vienna Lager was chosen
as the runner-up entry among 365 entries in the category. \sourceaha
\end{aboutblock}

\specifications{\styleviennalager}{\galtol{5.5}}{1.048}{1.013}{4.7~\%}{22}{\srmtoebc{9}}{60~min}{}

\begin{methodandtiming}
 
\begin{mashsteps}
\mashstep{\ftoc{154}}{60~min}
\end{mashsteps}

\begin{fermentationsteps}
\fermentationstep{\ftoc{50}}{5~days}
\fermentationstep{\ftoc{65}}{Raise to by 2.5~°C/12~hours; 5~days}
\fermentationstep{\ftoc{34}}{Reduce to by 3~°C/12~hours; 5~days}
\end{fermentationsteps}

\begin{directions}
Add Midnight Wheat with 10 minutes remaining for color adjustment with scant
roast impression. Calculate mash pH with base malts only. Target mash pH 5.3.
Fine with gelatin.
\end{directions}

\end{methodandtiming}

\recipebreak

\begin{ingredientsblock}

\begin{malts}
\malt{Avangard Vienna}{\lbtokg{8.5}}
\malt{Weyermann Barke Pilsner}{\lbtokg{3}}
\malt{Weyermann Melanoidin}{\lbtokg{0.25}}
\malt{Briess Midnight Wheat}{\oztog{1.5}}
\end{malts}

\begin{hops}
\hop{\hopmagnum}{12.5~\%}{60~min}{\oztog{0.5}}
\hop{\hopsaaz}{3.5~\%}{15~min}{\oztog{0.5}}
\hop{Whirlfloc Tablet}{}{15~min}{1}
\hop{Yeast Nutrient}{}{10~min}{--}
\end{hops}

\singleyeast{Imperial Yeast L13}

\end{ingredientsblock}

\end{recipe}

\end{recipe}
